Energy-Aware Planning-Scheduling for\\Autonomous Aerial Robots

### 2022-02-17 energy-planning.tex
implemented Hector's comments

\theoremstyle{definition}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{assm}[thm]{Assumption}
\newtheorem{cor}{Corollary}
\newtheorem{conj}{Conjecture}[section]
\newtheorem{defn}{Definition}[section]
\newtheorem{exmp}{Example}[section]
\newtheorem{pb}{Problem}[section]
\newtheorem{rem}{Remark}
\newtheorem{obs}{Observation}

@@

\begin{abstract}
  The letter presents a planning-scheduling approach for battery-powered autonomous aerial robots that plans a coverage path and schedules simultaneously onboard computational tasks. It derives a novel variable coverage motion robust to airborne constraints and an empirically motivated differential periodic energy model. The model is enhanced with the time and energy contribution of the path and tasks, utilizing a previously proposed automatic modeling tool. Accounting for uncertainty, an initial ``plan-schedule'' is re-planned and re-scheduled in the function of the battery autonomously and in-flight. While exploiting all the available resources, the approach remedies possible in-flight failure in case of unexpected battery drops, e.g., due to adverse atmospheric conditions, increases the overall fault tolerance, and improves the power savings.
\end{abstract}

\begin{IEEEkeywords}
  Aerial Systems: Perception and Autonomy, Optimization and Optimal Control, Planning, Scheduling and Coordination, Planning under Uncertainty
\end{IEEEkeywords}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}  %
\label{sec:intro}       %
                        %
\IEEEPARstart{U}{se cases} involving aerial robots span broadly. They compromise diverse planning and scheduling strategies and often require high autonomy under strict energy budgets. A typical instance is an aerial robot visiting each point in a given space~\cite{cabreira2019survey}, running assigned computational tasks, a problem in the literature under coverage path planning (CPP)~\cite{choset2001coverage,galceran2013survey}. Here, the aerial robot might detect ground patterns and notify other ground-based actors with little human interaction (see Figure~\ref{fig:il-abs}). Such use cases arise in, e.g., precision agriculture~\cite{hajjaj2014review}, where harvesting involves ground~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, damage prevention aerial robots~\cite{puri2017agriculture, daponte2019review}.
Microcontrollers and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks are frequently mounted onto the robots in these and many other scenarios~\cite{william2019aerial, peng2019evaluating,wang2020yolo,alexey2021autonomous}.
%In these and many others, the robot frequently mounts microcontroller and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks~\cite{william2019aerial, peng2019evaluating,wang2020yolo,alexey2021autonomous}. 
We refer to computational tasks that can be scheduled with an energy impact as computations. We are interested in the simultaneous energy optimization of motion plans and computations schedules in-flight and refer to it as energy-aware planning-scheduling. Generic mobile robotics studies that deal with planning-scheduling energy awareness are scarce~\cite{brateman2006energy,sudhakar2020balancing,lahijanian2018resource,ondruska2015scheduled} and focused on ground-based robots~\cite{mei2005case,sadrpour2013mission,lahijanian2018resource,ondruska2015scheduled,ho2019learning}. Yet, aerial robots are particularly affected by various energy considerations. Indeed it would be generally required to land to recharge the battery~\cite{zamanakos2020energy}. Such a state of practice has prompted us to propose the planning-scheduling approach for autonomous aerial robots, combining the past body of knowledge but addressing aerial robots' peculiarities such as the atmospheric, battery, and turning radius constraints. Numerical simulations and experimental data of both static and dynamic plans-schedules show improved power savings and fault tolerance with the aerial robots remedying in-flight failures. Fig.~\ref{fig:il-abs} illustrates the intuition: an aerial robot flies full plan-schedule~(\ref{sth:i}), that is optimized w.r.t. the battery~(\ref{sth:ii}), and altered due to, e.g., unexpected battery defects~(\ref{sth:iii}).

\begin{figure}[t]
  \centering
  \vspace*{-6.8ex}
  \begin{tikzpicture}
    \node[inner sep=0pt] () at (0,0)
        {\scriptsize \input{\figpath/new/il_abs.tikz}};
    \node[inner sep=0pt] () at (-2,-5.67)
        {\scriptsize \input{\figpath/il_abs_energy1.tikz}};
    \node[inner sep=0pt] () at (2.1,-5.67)
        {\scriptsize \input{\figpath/il_abs_spectrum1.tikz}};
  \end{tikzpicture}
  \caption{Illustrative example of planning-scheduling. An initial plan~(in~\ref{sth:i}) is re-planned in-flight computations-wise~(in~\ref{sth:ii}) and motion-wise~(in~\ref{sth:iii}). Follow the collected energy data of a physical aerial robot flying the coverage.}
  \label{fig:il-abs}
  \vspace*{-3.7ex}
\end{figure}

There are numerous planning approaches applied to a variety of robots. An instance is an algorithm selecting an energy-optimized trajectory~\cite{mei2004energy} by, e.g., maximizing the operational time~\cite{wahab2015energy}. Many apply to a small number of robots~\cite{kim2005energy} and focus exclusively on planning the trajectory~\cite{kim2008minimum}, despite compelling evidence of the energy influence of consumptions~\cite{mei2005case,ondruska2015scheduled,sudhakar2020balancing,brateman2006energy}. In view of the availability of powerful heterogeneous computing hardware~\cite{rizvi2017general}, the use of computations is further expected to increase in the foreseeable future~\cite{abramov2012real,satria2016real,jaramillo2019visual}. In this context, planning-scheduling energy awareness is a recent research direction. Early studies (2000--2010) varied hardware-dependent aspects, e.g., frequency, voltage, along with motion aspects, e.g., motor and travel velocities~\cite{mei2005case,brateman2006energy,zhang2007low,sadrpour2013mission} whereas the literature from the past decade derives energy-aware plans-schedules in broader terms. These include simultaneous considerations for planning-scheduling in perception~\cite{ondruska2015scheduled}, localization~\cite{lahijanian2018resource}, navigation~\cite{ho2019learning,ho2019qos,ho2018towards}, and anytime planning~\cite{sudhakar2020balancing}. We extend the relevant literature to the case of CPP with aerial robots.

Our focus is on fixed wings, i.e., airborne robots where wings provide lift, propellers forward thrust, and control surfaces maneuvering. Here, motion and computations energies are within an order of magnitude from each other~\cite{seewald2020mechanical}. Indeed there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations and vice-versa. The occurrence frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.) and lighter-than-air aerial robots (e.g., blimps). It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2018towards,ho2019learning,ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.

To guarantee energy awareness, our approach uses optimal control where both the paths and schedules variations are trajectories, varying between given bounds (i.e., physical constraints of the robot and computing hardware, the desired quality of the coverage, etc.). Numerous past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}, whereas some others greedy~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission} and reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards,ho2019learning}. Both the variations trajectories are derived for future time instants employing computations and motion energies and battery models. The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware energy modeling~\cite{seewald2019coarse,seewald2019component}, whereas the battery an equivalent circuit model (ECM) from the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}. The motion wraps the past two in a cohesive model that uses differential and periodic modeling to predict future energy behavior of various plans-schedules. In Fig.~\ref{fig:il-abs}, collected energy data (bottom left) and spectrum analysis (right) of a fixed-wing aerial robot flying CPP motivates the motion energy model: the evolution is periodic, an observation we exploit in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.

The remaining sections of the letter are then organized as follows. Sec.~\ref{sec:prob} provides basic constructs, such as the concepts of the plan, stages, triggering and final points, and path functions, as well as the problem formulation. Sec.~\ref{sec:algo} describes in detail the methodology of planning-scheduling. Sec.~\ref{sec:experimental} presents the results and showcases the performances, and Sec.~\ref{sec:conclusion} concludes and provides future perspectives. Appendices~\ref{app:proof-eqv}--\ref{app:proof-bat} provide supplementary material.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem Formulation}  %
\label{sec:prob}               %
                               %
\begin{figure}[t]
  \footnotesize
  \begin{minipage}[l]{0.35\columnwidth}
    \caption{Defs.~\ref{def:plan}--\hyperref[def:trigs]{4} on a slice of the plan $\Gamma$. $\mathbf{p}_{\Gamma_1},\dots$ are triggering points in which proximity happens change of stages $\Gamma_1,\dots$. Each contains a path function $\varphi_1,\dots$ and parameters to alter the path and schedule $c_{1,1},\dots$.}
    \label{fig:traj1}
  \end{minipage}\hfill
  \begin{minipage}[c]{0.6\columnwidth}
    \centering
    \vspace*{-4.5ex}
    \input{\figpath/new/traj1.tikz}
  \end{minipage}
  \vspace*{-4.5ex}
\end{figure}

Before defining the problem of energy-aware planning-scheduling in Sec.~\ref{sec:pbfor}, Sec.~\ref{sec:prelim} provides necessary preliminaries. For CPP and, e.g., pattern detections in precision agriculture, we assume that aerial robot travels a \emph{plan} with information about the path and the schedule.

\vspace*{-2ex}
\subsection{Preliminaries}
\label{sec:prelim}

\begin{defn}[Plan]\label{def:plan}
  Given a generic point $\mathbf{p}(t)\in\mathbb{R}^2$ w.r.t. a reference frame $\mathcal{O}_W$ of the aerial robot flying at a given altitude $h\in\mathbb{R}_{>0}$, the \emph{plan} is a finite state machine (FSM) $\Gamma$, where the state-transition function $s:\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage
  \begin{equation*}s(\Gamma_i,\mathbf{p}(t)):=\begin{cases}
    \Gamma_{i+j} & \exists j\in\mathbb{Z},\text{ if }\norm{\mathbf{p}(t)-\mathbf{p}_{\Gamma_i}}<\varepsilon_i\\
    \Gamma_i & \text{otherwise}
  \end{cases}.\end{equation*}
\end{defn}

Here, $\Gamma_i$ is a \emph{stage}, and $\mathbb{Z}$ denotes the set of integers. At each stage, the aerial robot travels a path and runs a schedule on the computing hardware. Both are to be altered in Sec.~\ref{sec:algo} within given boundaries with \emph{path}- and \emph{computations}-specific \emph{parameters}. $\varepsilon_i$ is a stage-dependent value detailed %along with $\mathbf{p}_{\Gamma_i}$ in and 
after Definition~\ref{def:trigs}.

\begin{defn}[Stage]\label{def:stage}
  The $i$th \emph{stage} $\Gamma_i$ at time instant $t$ of a plan $\Gamma$ is
  \begin{equation*}\begin{split}
    \Gamma_i:=\{\varphi_i(\mathbf{p}(t),c_i^\rho),c_i^\sigma\mid
    \,&\forall j\in\,[\rho]_{>0},\,c_{i,j}\,\,\,\,\,\,\,\in\mathcal{C}_{i,j},\,\\
      &\forall k\in[\sigma]_{>0},\,c_{i,\rho+k}\in\mathcal{S}_{i,k}\,\},
  \end{split}\end{equation*}
  where $c_i^\rho$ and $c_i^\sigma$ are $\rho$ \emph{path} and $\sigma$ \emph{computations parameters}. $\mathcal{C}_{i,j}:=[\underline{c}_{i,j},\overline{c}_{i,j}]\subseteq\mathbb{R}$ is the $j$th path parameter $c_{i,j}$ constraint set, and $\mathcal{S}_{i,k}:=[\underline{c}_{i,\rho+k},\overline{c}_{i,\rho+k}]\subseteq\mathbb{Z}_{\geq 0}$ is the $k$th computation parameter constraint set.
\end{defn}

The notation $[\,\cdot\,]$ denotes positive naturals up to $\cdot$\,, i.e., $\{0,1,\dots,\,\cdot\,\}$.
For a set $\mathbb{X}$, $\mathbb{X}_{\geq 0}$ then indicates it is positive, $\mathbb{X}_{> 0}$ strictly positive.

The function $\varphi_i$ is a \emph{path function} specifying the path. These are stage-dependent mathematical functions the aerial robot tracks as it travels %the motion for 
the coverage. The notation $[\underline{\,\cdot\,},\overline{\,\cdot\,}]$ denotes the upper/lower bounds of a parameter $\cdot\,$, i.e.,
\begin{equation}
  \underline{\,\cdot\,}\leq\,\cdot\,\leq\overline{\,\cdot\,}.
\end{equation}

@@

The stage-dependent value $\varepsilon_i\in\mathbb{R}_{\geq 0}$ in Def.~\ref{def:plan} expresses the radius of an imaginary circle over $\mathbf{p}_{\Gamma_i}$.

Fig.~\ref{fig:traj1} illustrates the concepts in Defs.~\ref{def:plan}--\hyperref[def:trigs]{4}. $\varphi_0,\dots,\varphi_5$ are path functions. $\varphi_0$ and $\varphi_4$ are circles, while $\varphi_1$, $\varphi_3$, and $\varphi_5$ are lines. They are relative to different stages $\Gamma_1,\dots$ but $\Gamma_0$, the starting stage, and are changed in the proximity of $\mathbf{p}_{\Gamma_0},\dots$. %The constraint set $\mathcal{C}_{4,1}$ forms the area where 
It is possible to alter the paths $\varphi_1,\dots,\varphi_4$ with the parameters $c_{1,1},\dots,c_{4,1}$; the gray area in the figure. %The area relative to $\Gamma_5$ is bounded by $\underline{c}_{5,1}\overline{c}_{5,1}$.

@@

Fig.~\ref{fig:state-machine-loop} illustrates  the concepts in Def.~\ref{def:primitive}. A plan composed of $n$ stages $\Gamma_1,\dots,\Gamma_n$ (containing primitive paths $\varphi_1,\dots,\varphi_n$) is reiterated with the shift $\mathbf{d}$. $t_1<\dots<t_4$ are time instant $\in\mathbb{R}_{> 0}$. $\Gamma_f$ is the accepting stage, indicating the plan is completed, $\Gamma_0$ the initial stage where the aerial robot, e.g., awaits the starting command.

\vspace*{-2ex}
\subsection{Energy-aware planning-scheduling problem}
\label{sec:pbfor}

The problem of planning-scheduling is composed of two sub-problems. One is to form a static plan that visits each point in space, the other to re-plan and re-schedule the plan in-flight in an energy-aware way.

\begin{pb}[Coverage problem]
  \label{pb:cov-pb}
  Consider a finite set of vertices of a polygon $v:=\{v_1,v_2,\dots\}$ where each vertex $v_i:=(x_{v_i},y_{v_i}),\forall i\in[|v|]_{>0}$
  %,\,o_{j,k}:=(x_{o_{j,k}},y_{o_{j,k}}),\,\forall j\in|o|,k\in|o_j|$ 
  is a point w.r.t. $\mathcal{O}_W$. Let $\underline{r}\in\mathbb{R}_{\geq 0}$, the minimum turning radius, and $\mathbf{p}(t_0)$, the starting point at the time instant $t_0$, be given. The \emph{coverage problem} is the problem of finding a plan $\Gamma$ that covers the polygon.
\end{pb}

For a set $\mathbb{X}$, the notation $|\mathbb{X}|$ denotes the cardinality of $\mathbb{X}$%, i.e, $|\mathbb{X}|:=\sum_{x\in\mathbb{X}}1$
.

\begin{pb}[Re-planning-scheduling problem]
  \label{pb}
  Consider an initial plan $\Gamma$ in Def.~\ref{def:plan}. The \emph{re-planning-scheduling problem} is the problem of finding the optimal configuration of path and computations parameters $c_i(t),\,\forall i\in\{1,2,\dots\}$ under energy constraints and uncertainty at each time step $t$.
\end{pb}

Here, $c_i$ denotes a row vector with both the path and computations parameters in sequence, i.e., $c_i:=[\begin{matrix}\,c_i^\rho & c_i^\sigma\,\end{matrix}]'$. The notation $\,\cdot\,'$ denotes the transpose of $\cdot\,$.

@@

%One can define the plan using primitive paths or define all the stages explicitly and find $n$ searching the value which satisfies the Eq.~(\ref{eq:primitive}). If there is no such value, (e.g., when the plan is composed of only one stage), the period $T$ from Def.~\ref{def:period} can be determined empirically from energy data (such as these shown in Fig.~\ref{fig:il-abs}).

%\begin{pb}[UAV planning problem]\label{pb}
%  Consider an initial plan $\Gamma$ from Def.~\ref{def:mission}. We are interested in the planning of the parameters $c_i,\,\forall i\in[l]^+$ and energy constraints and in the guidance of the UAV to the path resulting from such plan.
%\end{pb}

>>>>

\theoremstyle{definition}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{assm}[thm]{Assumption}
\newtheorem{cor}{Corollary}
\newtheorem{conj}{Conjecture}[section]
\newtheorem{defn}{Definition}[section]
\newtheorem{exmp}{Example}[section]
\newtheorem*{pb}{Problem}%[section]
\newtheorem{rem}{Remark}
\newtheorem{obs}{Observation}
\newtheorem*{ctb}{Contribution}

@@

\vspace*{-4.65ex}

\begin{abstract}
  This letter presents an online planning-scheduling approach for battery-powered autonomous aerial robots. The approach plans a coverage path and schedules simultaneously onboard computational tasks. It further derives a novel variable coverage motion robust to airborne constraints and an empirically motivated energy model. The model is enhanced with the energy contribution of the schedule, utilizing a previously proposed automatic modeling tool. Data show how an initial flight plan is adjusted online in the function of the available battery, accounting for uncertainty. Here, the proposed approach additionally remedies possible in-flight failure in case of unexpected battery drops, e.g., due to adverse atmospheric conditions, and increases the overall fault tolerance.
\end{abstract}

\begin{IEEEkeywords}
  Aerial Systems: Perception and Autonomy, %Optimization and Optimal Control, 
  Planning, %Scheduling and Coordination, 
  Planning under Uncertainty
\end{IEEEkeywords}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}  %
\label{sec:intro}       %
                        %
\IEEEPARstart{U}{se cases} involving aerial robots span broadly. They compromise diverse planning and scheduling strategies and often require high autonomy under strict energy budgets. 
An instance is coverage path planning (CPP) in the literature~\cite{choset2001coverage,galceran2013survey}, consisting of, e.g., an aerial robot visiting every point in a given space~\cite{cabreira2019survey}, running assigned computational tasks. Here, the aerial robot might detect ground patterns and notify other ground-based actors with little human interaction. Such use cases arise in, e.g., precision agriculture~\cite{hajjaj2014review}, where harvesting involves ground~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, damage prevention aerial robots~\cite{puri2017agriculture, daponte2019review}.
Microcontrollers and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks are frequently mounted onto the robots in these and many other scenarios~\cite{william2019aerial, peng2019evaluating,wang2020yolo,alexey2021autonomous}.
%In these and many others, the robot frequently mounts microcontroller and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks~\cite{william2019aerial, peng2019evaluating,wang2020yolo,alexey2021autonomous}. 
We refer to computational tasks that can be scheduled with an energy impact as computations. We are interested in the energy optimization of motion plans and computations schedules in-flight and refer to it as energy-aware planning-scheduling. Studies that deal with planning-scheduling energy awareness for mobile robots are scarce~\cite{brateman2006energy,sudhakar2020balancing,lahijanian2018resource,ondruska2015scheduled} and focused on ground-based robots~\cite{mei2005case,sadrpour2013mission,lahijanian2018resource,ondruska2015scheduled,ho2019learning}. Yet, aerial robots are particularly affected by various energy considerations. Indeed it would be generally required to land to recharge the battery. Such a state of practice has prompted us to propose the planning-scheduling approach for autonomous aerial robots, combining the past body of knowledge but addressing aerial robots' peculiarities such as the atmospheric, battery, and turning radius constraints. Numerical simulations and experimental data of both static and dynamic plans and schedules show improved power savings and fault tolerance with the aerial robots remedying in-flight failures. Fig.~\ref{fig:il-abs} illustrates the intuition: an aerial robot flies full plan and schedule~(\ref{sth:i}), that is optimized respecting the battery state~(\ref{sth:ii}), and altered due to, e.g., unexpected battery defects~(\ref{sth:iii}).

\begin{figure}[t]
  \centering
  \vspace*{-6.8ex}
  \begin{tikzpicture}
    \node[inner sep=0pt] () at (0,0)
        {\scriptsize \input{\figpath/new/il_abs.tikz}};
    \node[inner sep=0pt] () at (-2,-5.67)
        {\scriptsize \input{\figpath/il_abs_energy1.tikz}};
    \node[inner sep=0pt] () at (2.1,-5.67)
        {\scriptsize \input{\figpath/il_abs_spectrum1.tikz}};
  \end{tikzpicture}
  \caption{%Illustrative example of planning-scheduling. 
  An initial plan~(in~\ref{sth:i}) is re-planned online changing the resolution, detection rate, or other computational aspects~(in~\ref{sth:ii}) and changing the number of fly-byes or other motion aspects~(in~\ref{sth:iii}). Follow the collected energy data of a physical aerial robot flying the static coverage.}
  \label{fig:il-abs}
  \vspace*{-3.7ex}
\end{figure}

There are numerous planning approaches applied to a variety of robots. An instance is an algorithm selecting an energy-optimized trajectory~\cite{mei2004energy} by, e.g., maximizing the operational time~\cite{wahab2015energy}. Many apply to a small number of robots~\cite{kim2005energy} and focus exclusively on planning the trajectory~\cite{kim2008minimum}, despite compelling evidence of the energy influence of consumptions~\cite{mei2005case,ondruska2015scheduled,sudhakar2020balancing,brateman2006energy}. In view of the availability of powerful heterogeneous computing hardware~\cite{rizvi2017general}, the use of computations is further expected to increase in the foreseeable future~\cite{abramov2012real,satria2016real,jaramillo2019visual}. In this context, planning-scheduling energy awareness is a recent research direction. Early studies (2000--2010) varied hardware-dependent aspects, e.g., frequency, voltage, along with motion aspects, e.g., motor and travel velocities~\cite{mei2005case,brateman2006energy,zhang2007low,sadrpour2013mission} whereas the literature from the past decade derives energy-aware plans-schedules in broader terms. These include simultaneous considerations for planning-scheduling in perception~\cite{ondruska2015scheduled}, localization~\cite{lahijanian2018resource}, navigation~\cite{ho2019learning,ho2019qos,ho2018towards}, and anytime planning~\cite{sudhakar2020balancing}.

Our focus is on fixed wings, i.e., airborne robots where wings provide lift, propellers forward thrust, and control surfaces maneuvering. Here, motion and computations energies are within an order of magnitude from each other~\cite{seewald2020mechanical}. Indeed there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations and vice-versa. The occurrence frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.) and lighter-than-air aerial robots (e.g., blimps). It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2018towards,ho2019learning,ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
\begin{ctb}
  We extend the literature on planning-schedu- ling to CPP with aerial robots, model the overall and computations energies, and battery evolution, and derive a variable coverage motion for constrained systems, e.g., fixed wings.
\end{ctb}

To guarantee energy awareness, our approach uses optimal control where both the paths and schedules variations are trajectories, varying between given bounds (i.e., physical constraints of the robot and computing hardware, the desired quality of the coverage, etc.). Numerous past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}, whereas some others greedy~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission} and reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards,ho2019learning}. Both the variations trajectories are derived for future time instants employing computations and overall energies and battery models. The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware energy modeling~\cite{seewald2019coarse,seewald2019component}, whereas the battery an equivalent circuit model (ECM) from the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}. The overall wraps the past two in a cohesive model that uses differential and periodic modeling to predict future energy behavior of different plans and schedules. In Fig.~\ref{fig:il-abs}, collected energy data (bottom left) and spectrum analysis (right) of a fixed-wing aerial robot flying CPP motivates the overall energy model: the evolution is periodic, an observation we exploit in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.

The remaining sections of the letter are then organized as follows. Section~\ref{sec:prob} provides basic constructs, such as the concepts of the stages, path functions, triggering and final points, and plan, as well as the problem formulation. Section~\ref{sec:algo} describes in detail the methodology of planning-scheduling. Section~\ref{sec:experimental} presents the results and showcases the performances, and Section~\ref{sec:conclusion} concludes and provides future perspectives. %Appendices~\ref{app:proof-eqv}--\ref{app:proof-bat} provide supplementary material.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem Formulation}  %
\label{sec:prob}               %
                               %
\begin{figure}[t]
  \footnotesize
  \begin{minipage}[l]{0.35\columnwidth}
    \caption{Definitions~\ref{def:stage}--\hyperref[def:plan]{4} on a slice of the plan $\Gamma$. $\mathbf{p}_{\Gamma_i}$ are triggering points in which proximity happens change of stages $\Gamma_i$. Each contains a path function $\varphi_i$ and $j$ parameters to alter the path and schedule $c_{i,1},\dots,c_{i,j}$.}
    \label{fig:traj1}
  \end{minipage}\hfill
  \begin{minipage}[c]{0.6\columnwidth}
    \centering
    \vspace*{-4.5ex}
    \input{\figpath/new/traj1.tikz}
  \end{minipage}
  \vspace*{-4.5ex}
\end{figure}

Before defining the problem of energy-aware planning-scheduling in Section~\ref{sec:pbfor}, Section~\ref{sec:prelim} provides necessary preliminaries. For CPP and, e.g., pattern detections in precision agriculture, we assume that aerial robot travels a \emph{plan} composed of \emph{stages}. At each stage, the aerial robot travels a path and runs a schedule on the computing hardware. Both are to be altered in Section~\ref{sec:algo} within given boundaries with \emph{path}- and \emph{computations}-specific \emph{parameters}.%with information about the path and the schedule.

\subsection{Preliminaries}
\label{sec:prelim}

%Here, $\Gamma_i$ is a \emph{stage}, $\varepsilon_i$ is a stage-dependent value detailed 
%along with $\mathbf{p}_{\Gamma_i}$ in and 
%after Definition~\ref{def:trigs}.

\begin{defn}[Stage]\label{def:stage}
  Given a generic point $\mathbf{p}\in\mathbb{R}^2$ w.r.t. a reference frame $\mathcal{O}_W$ of the aerial robot flying at a given altitude $h\in\mathbb{R}_{>0}$, the $i$th \emph{stage} $\Gamma_i$ at time instant $t$ %of a plan $\Gamma$ 
  is
  \begin{equation*}\begin{split}
    \Gamma_i:=\{\varphi_i(\mathbf{p}(t),c_i^\rho),c_i^\sigma\mid
    \,&\forall j\in\,[\rho]_{>0},\,c_{i,j}\,\,\,\,\,\,\,\in\mathcal{C}_{i,j},\,\\
      &\forall k\in[\sigma]_{>0},\,c_{i,\rho+k}\in\mathcal{S}_{i,k}\,\},
  \end{split}\end{equation*}
  where $c_i^\rho$ and $c_i^\sigma$ are $\rho$ \emph{path} and $\sigma$ \emph{computations parameters}. $\mathcal{C}_{i,j}:=[\underline{c}_{i,j},\overline{c}_{i,j}]\subseteq\mathbb{R}$ is the $j$th path parameter $c_{i,j}$ constraint set, and $\mathcal{S}_{i,k}:=[\underline{c}_{i,\rho+k},\overline{c}_{i,\rho+k}]\subseteq\mathbb{Z}_{\geq 0}$ is the $k$th computation parameter constraint set.
\end{defn}

For a set $\mathbb{X}$, $\mathbb{X}_{\geq 0}$ then indicates it is positive, $\mathbb{X}_{> 0}$ strictly positive, and $|\mathbb{X}|$ its cardinality. $\mathbb{Z},\mathbb{R}$ are the sets of integers and reals.% respectively.

The notation $[\,\cdot\,]$ denotes positive naturals up to $\cdot$\,, i.e., $\{0,1,\dots,\,\cdot\,\}$, $\,\cdot\,'$ the transpose of $\cdot\,$, and $[\underline{\,\cdot\,},\overline{\,\cdot\,}]$ the upper/lower bounds of a parameter $\cdot\,$, i.e.,
\begin{equation}
  \underline{\,\cdot\,}\leq\,\cdot\,\leq\overline{\,\cdot\,}.
\end{equation}

The function $\varphi_i$ is a \emph{path function} specifying the path. These are stage-dependent mathematical functions the aerial robot tracks as it travels %the motion for 
the coverage.

@@

The plan merges the concepts from Definitions~\ref{def:stage}--\hyperref[def:trigs]{3}. %via a .

\begin{defn}[Plan]\label{def:plan}
  The \emph{plan} is a finite state machine (FSM) $\Gamma$, where the state-transition function $s:\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage
  \begin{equation*}s(\Gamma_i,\mathbf{p}(t)):=\begin{cases}
    \Gamma_{i+j} & \exists j\in\mathbb{Z},\text{ if }\norm{\mathbf{p}(t)-\mathbf{p}_{\Gamma_i}}<\varepsilon_i\\
    \Gamma_i & \text{otherwise}
  \end{cases}.\end{equation*}
\end{defn}

The stage-dependent value $\varepsilon_i\in\mathbb{R}_{\geq 0}$ in Definition~\ref{def:plan} expresses the radius of an imaginary circle over $\mathbf{p}_{\Gamma_i}$.

Fig.~\ref{fig:traj1} illustrates the concepts in Definitions~\ref{def:stage}--\hyperref[def:plan]{4}. $\varphi_0,\dots,\varphi_5$ are path functions. $\varphi_0$ and $\varphi_4$ are circles, while $\varphi_1$, $\varphi_3$, and $\varphi_5$ are lines. They are relative to different stages $\Gamma_1,\dots$ but $\Gamma_0$, the starting stage, and are changed in the proximity of $\mathbf{p}_{\Gamma_0},\dots$. %The constraint set $\mathcal{C}_{4,1}$ forms the area where 
It is possible to alter the paths $\varphi_1,\dots,\varphi_4$ with the parameters $c_{1,1},\dots,c_{4,1}$; the gray area in the figure. %The area relative to $\Gamma_5$ is bounded by $\underline{c}_{5,1}\overline{c}_{5,1}$.

@@

Fig.~\ref{fig:state-machine-loop} illustrates  the concepts in Definition~\ref{def:primitive}. A plan composed of $n$ stages $\Gamma_1,\dots,\Gamma_n$ (containing primitive paths $\varphi_1,\dots,\varphi_n$) is reiterated with the shift $\mathbf{d}$. $t_1<\dots<t_4$ are time instants $\in\mathbb{R}_{> 0}$. $\Gamma_f$ is the accepting stage, indicating the plan is complete, $\Gamma_0$ the initial stage where the aerial robot, e.g., awaits the starting command.

\subsection{Energy-aware planning-scheduling problem}
\label{sec:pbfor}

The problem of planning-scheduling is composed of two sub-problems. One is to form a static plan that visits every point in space, the other to re-plan and re-schedule the plan in-flight in an energy-aware way.

\begin{pb}[Coverage and re-planning-scheduling problem]
  \label{pb:cov-pb}
  Consider a finite set of vertices of a polygon $v:=\{v_1,v_2,\dots\}$ where each %vertex $v_i:=(x_{v_i},y_{v_i})%,\forall i\in[|v|]_{>0}$
  %,\,o_{j,k}:=(x_{o_{j,k}},y_{o_{j,k}}),\,\forall j\in|o|,k\in|o_j|$ 
  is a point w.r.t. $\mathcal{O}_W$. 
  Let $\underline{r}\in\mathbb{R}_{\geq 0}$, the vehicle's turning radius, and $\mathbf{p}(t_0)$, the starting point at the time instant $t_0$, be given. 
  The \emph{coverage problem} is the problem of finding a plan $\Gamma$ to cover the polygon, whereas the \emph{re-planning-scheduling problem} the optimal parameters $c_i$ in time.
\end{pb}

%, i.e, $|\mathbb{X}|:=\sum_{x\in\mathbb{X}}1$
%.

%\begin{pb}[Re-planning-scheduling problem]
%  \label{pb}
%  Consider an initial plan $\Gamma$ in Definition~\ref{def:plan}. The \emph{re-planning-scheduling problem} is the problem of finding the optimal configuration of path and computations parameters $c_i(t),\,\forall i\in\{1,2,\dots\}$ under energy constraints and uncertainty at each time step $t$.
%\end{pb}

Here, $c_i$ denotes a row vector with both the path and computations parameters in sequence, i.e., $c_i:=[\begin{matrix}\,c_i^\rho & c_i^\sigma\,\end{matrix}]'$. %The notation .

@@

%One can define the plan using primitive paths or define all the stages explicitly and find $n$ searching the value which satisfies the Eq.~(\ref{eq:primitive}). If there is no such value, (e.g., when the plan is composed of only one stage), the period $T$ from Definition~\ref{def:period} can be determined empirically from energy data (such as these shown in Fig.~\ref{fig:il-abs}).

%\begin{pb}[UAV planning problem]\label{pb}
%  Consider an initial plan $\Gamma$ from Definition~\ref{def:mission}. We are interested in the planning of the parameters $c_i,\,\forall i\in[l]^+$ and energy constraints and in the guidance of the UAV to the path resulting from such plan.
%\end{pb}
